Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-28 paper/paper.tex
Some more things to write
More

\begin{algorithm*}[tb]
\DontPrintSemicolon
\begin{multicols}{2}
\nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\loopcomp{\mathcal{P}},
        \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}},$
        \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
    \mathcal{T}^{2,2}), (\mathcal{P}^{3 + k,2},\ \mathcal{T}^{3,2}) \big]$ \;
    \nl \ForEach{$v \in \V(\mathcal{P})$}{
        \nl $D_v \gets \V(\mathcal{T})$\;
        \nl \ForEach{$(P,\,T) \in L$}{
            \nl $D_v \gets \{ w \in D_v : $ \\
            \hspace*{4em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
            \hspace*{4em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
        }
        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$
    }
    \nl \lIf{\FuncSty{propagate}(L, D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
    \nl \lElse{$\KwSty{return}~\KwSty{false}$}
}
\bigskip
\nl $\FuncSty{search}$ (GraphPairs $L$, Domains $D$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;
    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried\label{line:sym}}}{
            \nl \KwSty{continue} \;
        }
        \nl $D' \gets \FuncSty{clone}(D)$ \;
        \nl $D'_v \gets \{ v' \} $ \;
        \nl \If{\FuncSty{propagate}(L, D')}{
            \nl \If{$\FuncSty{search}(L, \{ D \in D' : \left|D\right| > 1 \}, k)$}{
                \nl $\KwSty{return}~\KwSty{true}$ \;
            }
        }
    }
}
\bigskip
\nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \While{\KwSty{true}}{
        \nl \If{\textnormal{no effectively-unit domains remain (treating all wildcard~values as a single
            value)\label{line:effect}}}{
            \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
                \nl $\KwSty{return}~\KwSty{false}$ \;
            }
        }
        \nl \If{\textnormal{no effectively-unit domains remain}}{
            \nl $\KwSty{return}~\KwSty{true}$ \;
        }
        \nl $D_v \gets \textnormal{an effectively-unit domain from}~D$ \;
        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard~value if there is more
        than one \;
        \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{
            \nl $D_w \gets D_w \setminus \{ v' \}$ \label{line:removev} \;
            \nl \ForEach{$(P,\,T) \in L$}{
                \nl \If{$v \sim_P w$}{
                    \nl $D_w \gets D_w \cap \left(\N_T(v') \cup \textnormal{wildcards}\right)$
                }
            }
            \nl \lIf{$D_w = \emptyset$}{$\KwSty{return}~\KwSty{false}$}
        }
    }
}
\bigskip
\nl $\FuncSty{allDifferent}$ (Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
\nl $(H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,0)$ \;
\nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
    \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
    \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
    \nl \lIf{$D_v = \emptyset~\KwSty{or}~\left|A\right| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
    \nl \lIf{$\left|A\right| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
}
\nl $\KwSty{return}~\KwSty{true}$ \;
}
\end{multicols}
\caption{An algorithm for the $k$-less subgraph isomorphism problem.}
\label{algorithm:sip}
\end{algorithm*}

@@

@@

?? Constraints and unit propagation

@@

?? All different

We must be careful to treat domains containing multiple wildcard values (which we call ``effectively
unit'') specially during unit propagation (line~\ref{line:effect}), and we introduce a symmetry
break (line~\ref{line:sym}) to try only a single wildcard value for each variable.

?? Search. No backjumping.

>>>>

\begin{algorithm*}[tb]
\DontPrintSemicolon
\begin{multicols}{2}
\nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\loopcomp{\mathcal{P}},
        \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}},$
        \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
    \mathcal{T}^{2,2}), (\mathcal{P}^{3 + k,2},\ \mathcal{T}^{3,2}) \big]$ \;
    \nl \ForEach{$v \in \V(\mathcal{P})$}{
        \nl $D_v \gets \V(\mathcal{T})$\;
        \nl \ForEach{$(P,\,T) \in L$}{
            \nl $D_v \gets \{ w \in D_v : $ \\
            \hspace*{4em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
            \hspace*{4em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
        }
        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$
    }
    \nl \If{\FuncSty{propagate}(L, D)}{
        \nl $\KwSty{return}~\FuncSty{search}(L, \{ E \in D : \left|E\right| > 1 \}, k)$\;
    }
    \nl \lElse{$\KwSty{return}~\KwSty{false}$}
}
\bigskip
\nl $\FuncSty{search}$ (GraphPairs $L$, Domains $D$, Int $k$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;
    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried\label{line:sym}}}{
            \nl \KwSty{continue} \;
        }
        \nl $D' \gets \FuncSty{clone}(D)$ \;
        \nl $D'_v \gets \{ v' \} $ \;
        \nl \If{\FuncSty{propagate}(L, D')}{
            \nl \If{$\FuncSty{search}(L, \{ E \in D' : \left|E\right| > 1 \}, k)$}{
                \nl $\KwSty{return}~\KwSty{true}$ \;
            }
        }
    }
}
\bigskip
\nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
    \nl \While{\KwSty{true}}{
        \nl \If{\textnormal{no effectively-unit domains remain (treating all wildcard~values as a single
            value)\label{line:effect}}}{
            \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
                \nl $\KwSty{return}~\KwSty{false}$ \;
            }
        }
        \nl \If{\textnormal{no effectively-unit domains remain}}{
            \nl $\KwSty{return}~\KwSty{true}$ \;
        }
        \nl $D_v \gets \textnormal{an effectively-unit domain from}~D$ \;
        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard~value if there is more
        than one \;
        \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{
            \nl $D_w \gets D_w \setminus \{ v' \}$ \label{line:removev} \;
            \nl \ForEach{$(P,\,T) \in L$}{
                \nl \If{$v \sim_P w$}{
                    \nl $D_w \gets D_w \cap \left(\N_T(v') \cup \textnormal{wildcards}\right)$
                }
            }
            \nl \lIf{$D_w = \emptyset$}{$\KwSty{return}~\KwSty{false}$}
        }
    }
}
\bigskip
\nl $\FuncSty{allDifferent}$ (Domains $D$) $\rightarrow$ Bool \;
\nl \Begin{
\nl $(H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,0)$ \;
\nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
    \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
    \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
    \nl \lIf{$D_v = \emptyset~\KwSty{or}~\left|A\right| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
    \nl \lIf{$\left|A\right| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
}
\nl $\KwSty{return}~\KwSty{true}$ \;
}
\end{multicols}
\vspace{0.5cm}% Do not remove! Otherwise, the caption overlaps the algorithm due to algorithm2e and
% multicol[vlined] not being entirely happy with each other.
\caption{A bit-parallel algorithm for the $k$-less subgraph isomorphism problem.}
\label{algorithm:sip}
\end{algorithm*}

@@

?? Bit parallel.

@@

We begin by trying to infer domain deletions. The ?? function looks for domains which contains
either only a single value, or only wildcards---we call such a domain ``effectively-unit''. If such
a domain $D_v$ exists, we eliminate its value from every other domain, and then propagate adjacency:
for each domain corresponding to a vertex adjacent to $v$, we eliminate any value from its domain
which is not adjacent to $v$ (treating wildcards as being adjacent to all vertices). If a domain
wipeout occurs, we return failure.

@@

If no effectively-unit domains remain, we attempt stronger propagation for the all-different
constraint. Our ?? function is the bit-parallel propagator taken from
\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? which
guarantees generalised arc consistency. ?? a bit more on how it works. It can easily be seen that
this propagator will always find Hall sets or failed Hall sets of size zero or one, but it may miss
larger sets. This propagation could create new effectively-unit domains; if so, we loop.

?? Search

we introduce a symmetry
break (line~\ref{line:sym}) to try only a single wildcard value for each variable.
